Algorithm Engineering

### 2022-11-16 Assignments/paper.tex
update

>>>>

\subsection{Explain how divide and conquer algorithms can be parallelized with tasks in OpenMP.}
\subsection{Describe some ways to speed up merge sort.}
\subsection{What is the idea behind multithreaded merging?}
\subsection{Read What every systems programmer should know about concurrency. https://assets.bitbashing.io/papers/concurrency- primer.pdf
Discuss two things you find particularly interesting.}
